### 2018-06-05 Maths Notes/Further Pure/FP2/Cheat Sheet/FP2 Cheat Sheet.tex
FP2 Notes

\subsection{Loci on the complex plane}
{\renewcommand{\arraystretch}{2}
\begin{tabularx}{\textwidth}{|X|X|}
\hline
Equation&Description\\
\hline
{\Large$|z-z_1|=r$}&A circle centre $(x_1,y_1)$ with a radius r\\
\hline
{\Large$|z-z_1|=|z-z_2|$}&A perpendicular bisector of the line segment joining points $z_1$ and $z_2$\\
\hline
{\Large$|z-z_1|=\lambda|z-z_2|$}&A circle, the equation of which is best found algebraically\\
\hline
{\Large$\arg(z-z_1)=\theta$}&The half line from a fixed point $z_1$, making an angle $\theta$ with the positive real axis\\
\hline
{\Large$\arg(\frac{z-z_1}{z-z_2})=\theta$}&An arc between the points $z_1$ and $z_2$ where the angle the lines from $z_1$ and $z_2$ to any point on the arc is $\theta$\\
\hline
\end{tabularx}}
\subsubsection{Cartesian equations of loci}
Method for modulus questions:
\begin{itemize}
\item Replace $z$ with $x+iy$
\item Group real and imaginary parts if needed
\item Use $|x+iy|=\sqrt{x^2+y^2}$
\item Complete the square if you know you're going to get a circle
\end{itemize}

\subsection{Translations}
\begin{itemize}
\item $w=z+a+ib$ represents a translation with translation vector $\begin{pmatrix}
a\\b
\end{pmatrix}$
\item $w=kz$ represents an enlargement with scale factor $k$ centre $(0,0)$
\item $w=kz+a+ib$ represents an enlargement scale factor $k$ centre $(0,0)$ followed by a translation with translation vector $\begin{pmatrix}
a\\b
\end{pmatrix}$
\item $w=z^2$ multiply a shape by itself, for example a circle of radius 4 would go to radius 16
\end{itemize}

\section{First order differential equations}
\subsection{Solving first order DE using an integrating factor}
Solving $\dfrac{dy}{dx}+P(x)y=Q(x)$\\
\\
IF(Integrating factor) is found by finding $\mathlarger{e^{\int p(x) \ dx}}$ And multiplying the DE by the IF.\\
\\
This will result in the DE being in the form:
$$f(x)\frac{dy}{dx}+f'(x)y$$
This form can then be shortened by integrating:
$$\int f'(x)g(x)+f(x)g'(x) dx=f(x)g(x)+c$$
Integrate both sides then simplify
\section{Second order differential equations}
{\renewcommand{\arraystretch}{2}
\begin{tabularx}{\textwidth}{|X|X|X|}
\hline
\textbf{Solution to auxiliary equation}&\textbf{General solution}&\textbf{Trig general solution}\\
\hline
Two real roots $b^2>4ac$&$Ae^{\alpha x}+Be^{\beta x}$&\\
\hline
One real root $b^2=4ac$&$(A+bx)e^{\alpha x}$&\\
\hline
Imaginary only root $b^2<4ac$&$Ae^{\alpha x}+Be^{-\alpha x}$&
$p\cos\alpha x+q\sin\alpha x$
\\
\hline
Complex root $b^2<4ac$&$Ae^{(\beta+\alpha i)x}+Be^{(\beta-\alpha i)x}$&
$e^{\beta x}(p\cos\alpha x+q\sin\alpha x)$
\\
\hline
\end{tabularx}}
P=A+B\\
Q=i(A+B)
\subsection{Second ODE=f(x)}
\subsubsection{Standard forms of f(x)}
$f(x)=\lambda$\\
$f(x)=\lambda+\mu x$\\
$f(x)=\lambda+\mu x+\nu x^2$\\
$f(x)=ke^{px}$\\
$f(x)=m\cos\omega x$\\
$f(x)=m\sin\omega x$\\
$f(x)=m\cos\omega x\pm n\sin\omega x$
\\
To solve these find $\frac{dy}{dx}$ and $\frac{d^2y}{dx^2}$ and substitute them into the Second ODE, solving for the unknowns, then add them to the general solution.\\
\\
If there is a clash of terms between the CF and PI, then an alternate PI will be given to you. If in doubt, multiply the standard form through by x, but this will not always work.
\subsection{Boundary conditions}
If boundary conditions are given to you, the values of the unknowns can be found. Substitute the boundary conditions in and rearrange to find unknowns.
\newpage
\subsection{Substitution}
Transformations can be used to simplify differential equations, leaving $\frac{d^2y}{dx^2}$ with no coefficient.\\
Method:\\
\textcolor{red}{\large Find $\frac{dy}{dx}$ in terms of $\frac{dy}{du}$}
$$x=e^u \quad \frac{dx}{du}=e^u \quad \frac{du}{dx}=e^{-u} \quad 
\frac{dy}{dx}=\frac{dy}{du}\times\frac{du}{dx}=\mathbf{e^{-u}\frac{dy}{du}}
$$
\textcolor{red}{\large Find $\frac{d^2y}{dx^2}$ in terms of $\frac{d^2y}{du^2}$ and $\frac{dy}{du}$}\\
\textcolor{red}{Find $\frac{dy}{du}\Big(\frac{dy}{dx}\Big)$ by applying the product rule}
$$\frac{dy}{du}\Big(\frac{dy}{dx}\Big)=-e^{-u}\frac{dy}{du}+e^{-u}\frac{d^2y}{du^2}$$
\textcolor{red}{Multiply through by $\frac{du}{dx}$ to find the value of $\frac{d^2y}{dx^2}$}
$$\frac{d^2y}{dx^2}=\frac{dy}{du}\Big(\frac{dy}{dx}\Big)\times\frac{du}{dx}$$
$$\frac{d^2y}{dx^2}=e^{-u}\Big(-e^{-u}\frac{dy}{du}+e^{-u}\frac{d^2y}{du^2}\Big)$$
$$\frac{d^2y}{dx^2}=\mathbf{e^{-2u}\Big(-\frac{dy}{du}+\frac{d^2y}{du^2}\Big)}$$
\textcolor{red}{Then substitute the values for x,$\frac{dy}{dx}$, and $\frac{d^2y}{dx^2}$ into the original equation to simplify it}

>>>>

\subsection{Loci on the complex plane}
{\renewcommand{\arraystretch}{2}
\begin{tabularx}{\textwidth}{|X|X|}
\hline
Equation&Description\\
\hline
{\Large$|z-z_1|=r$}&A circle centre $(x_1,y_1)$ with a radius r\\
\hline
{\Large$|z-z_1|=|z-z_2|$}&A perpendicular bisector of the line segment joining points $z_1$ and $z_2$\\
\hline
{\Large$|z-z_1|=\lambda|z-z_2|$}&A circle, the equation of which is best found algebraically\\
\hline
{\Large$\arg(z-z_1)=\theta$}&The half line from a fixed point $z_1$, making an angle $\theta$ with the positive real axis\\
\hline
{\Large$\arg(\frac{z-z_1}{z-z_2})=\theta$}&An arc between the points $z_1$ and $z_2$ where the angle the lines from $z_1$ and $z_2$ to any point on the arc is $\theta$\\
\hline
\end{tabularx}}
\subsubsection{Cartesian equations of loci}
Method for modulus questions:
\begin{itemize}
\item Replace $z$ with $x+iy$
\item Group real and imaginary parts if needed
\item Use $|x+iy|=\sqrt{x^2+y^2}$
\item Complete the square if you know you're going to get a circle
\end{itemize}
Argument equations:
For lines, check by looking at the graph, but use
$$\frac{Im}{R_e}=\tan\theta$$
Remove the i from the imaginary part when putting it in the fraction, but remember that x and y are supposed to stay\\
For circles, find the centre and radius, and use this to form the equation, though remember to include $y>0$, where often necessary as it is an arc from the x axis
\subsection{Translations}
\begin{itemize}
\item $w=z+a+ib$ represents a translation with translation vector $\begin{pmatrix}
a\\b
\end{pmatrix}$
\item $w=kz$ represents an enlargement with scale factor $k$ centre $(0,0)$
\item $w=kz+a+ib$ represents an enlargement scale factor $k$ centre $(0,0)$ followed by a translation with translation vector $\begin{pmatrix}
a\\b
\end{pmatrix}$
\item $w=z^2$ multiply a shape by itself, for example a circle of radius 4 would go to radius 16
\end{itemize}

\section{First order differential equations}
\subsection{Solving first order DE using an integrating factor}
Solving $\dfrac{dy}{dx}+P(x)y=Q(x)$\\
\\
IF(Integrating factor) is found by finding $\mathlarger{e^{\int p(x) \ dx}}$ And multiplying the DE by the IF.\\
\\
This will result in the DE being in the form:
$$f(x)\frac{dy}{dx}+f'(x)y$$
This form can then be shortened by integrating:
$$\int f'(x)g(x)+f(x)g'(x) dx=f(x)g(x)+c$$
Integrate both sides then simplify
\section{Second order differential equations}
{\renewcommand{\arraystretch}{2}
\begin{tabularx}{\textwidth}{|X|X|X|}
\hline
\textbf{Solution to auxiliary equation}&\textbf{General solution}&\textbf{Trig general solution}\\
\hline
Two real roots $b^2>4ac$&$Ae^{\alpha x}+Be^{\beta x}$&\\
\hline
One real root $b^2=4ac$&$(A+bx)e^{\alpha x}$&\\
\hline
Imaginary only root $b^2<4ac$&$Ae^{\alpha x}+Be^{-\alpha x}$&
$p\cos\alpha x+q\sin\alpha x$
\\
\hline
Complex root $b^2<4ac$&$Ae^{(\beta+\alpha i)x}+Be^{(\beta-\alpha i)x}$&
$e^{\beta x}(P\cos\alpha x+Q\sin\alpha x)$
\\
\hline
\end{tabularx}}
P=A+B\\
Q=i(A+B)
\subsection{Second ODE=f(x)}
\subsubsection{Standard forms of f(x)}
$f(x)=\lambda$\\
$f(x)=\lambda+\mu x$\\
$f(x)=\lambda+\mu x+\nu x^2$\\
$f(x)=ke^{px}$\\
$f(x)=m\cos\omega x$\\
$f(x)=m\sin\omega x$\\
$f(x)=m\cos\omega x\pm n\sin\omega x$
\\
To solve these find $\frac{dy}{dx}$ and $\frac{d^2y}{dx^2}$ and substitute them into the Second ODE, solving for the unknowns, then add them to the general solution.\\
\\
If there is a clash of terms between the CF and PI, then an alternate PI will be given to you. If in doubt, multiply the standard form through by x, but this will not always work.
\subsection{Boundary conditions}
If boundary conditions are given to you, the values of the unknowns can be found. Substitute the boundary conditions in and rearrange to find unknowns.
\newpage
\subsection{Substitution}
Transformations can be used to simplify differential equations, leaving $\frac{d^2y}{dx^2}$ with no coefficient.\\
Method:\\
\textcolor{red}{\large Find $\frac{dy}{dx}$ in terms of $\frac{dy}{du}$}
$$x=e^u \quad \frac{dx}{du}=e^u \quad \frac{du}{dx}=e^{-u} \quad 
\frac{dy}{dx}=\frac{dy}{du}\times\frac{du}{dx}=\mathbf{e^{-u}\frac{dy}{du}}
$$
\textcolor{red}{\large Find $\frac{d^2y}{dx^2}$ in terms of $\frac{d^2y}{du^2}$ and $\frac{dy}{du}$}\\
\textcolor{red}{Find $\frac{dy}{du}\Big(\frac{dy}{dx}\Big)$ by applying the product rule}
$$\frac{dy}{du}\Big(\frac{dy}{dx}\Big)=-e^{-u}\frac{dy}{du}+e^{-u}\frac{d^2y}{du^2}$$
\textcolor{red}{Multiply through by $\frac{du}{dx}$ to find the value of $\frac{d^2y}{dx^2}$}
$$\frac{d^2y}{dx^2}=\frac{dy}{du}\Big(\frac{dy}{dx}\Big)\times\frac{du}{dx}$$
$$\frac{d^2y}{dx^2}=e^{-u}\Big(-e^{-u}\frac{dy}{du}+e^{-u}\frac{d^2y}{du^2}\Big)$$
$$\frac{d^2y}{dx^2}=\mathbf{e^{-2u}\Big(-\frac{dy}{du}+\frac{d^2y}{du^2}\Big)}$$
\textcolor{red}{Then substitute the values for x,$\frac{dy}{dx}$, and $\frac{d^2y}{dx^2}$ into the original equation to simplify it}
